---
title: "hypotheses_testing_vgsales"
output: html_document
---
Reading in and cleaning the data
```{r, include=FALSE}
library(dplyr)
library(e1071)
library(gridExtra)
library(ggplot2)

theme_set(theme_bw())

#reading in the data
df <- read.csv("vgsales.csv")

#since df contains 16k observations, lets limit the data to one year
df <- 
  df %>%
  filter(Year == '2016')

#don't want to visualize games with 0 sales so let's remove that
df <-
  df %>% 
  filter(NA_Sales > 0) 
``` 

Milestone 7: Hypothesis Testing
Decide on and test 3 hypotheses about your data.  You can choose the alpha.  Upload your code to GitHub.  Write a paragraph describing what you tested and summarizing the results of your tests on your website.

```{r}


```

Milestone 8: Regression or other analysis
Perform a statistical analysis of your choice on your data.  This can be computing a regression line, computing one of the previous analyses on a subset of the data, an analysis of variance (ANOVA) test, or any other statistical test.  Write a paragraph briefly describing the analysis and the results on your website and upload the code to GitHub.

perform ANOVA on average NA sales grouped by top 3 video game platforms
```{r}

#making a smaller dataframe for analysis of variance
anova1_df <- 
  df %>% 
  #top 3 platforms: PS4, Xbox One, and 3DS
  filter(Platform == "PS4" | Platform == "XOne" | Platform == "3DS") %>%
  #only kept the platform type and the sales
  select(Platform, NA_Sales)

#make a boxplot of the smaller data
anova1_plot <- 
  anova1_df %>%
  ggplot(aes(Platform, NA_Sales)) + 
  geom_boxplot() +
  xlab('Top 3 Platforms') +
  ylab('Sales in North America') +
  labs(title = 'Boxplot of Top 3 Platforms')

#display the anova table
anova1_platform <- aov(NA_Sales ~ Platform, data = anova1_df)
summary(anova1_platform)

#display the grand mean and all group means, plus group sizes
model.tables(anova1_platform, "means")

#perform turkey's honest significant different test as post-hoc analysis
anova1_posthoc <- TukeyHSD(anova1_platform)

#result of analysis gives difference of means, and upper and lower values
#of confidence interval, and adjusted p-values for htat pair of groups
plot(anova1_posthoc)

```

Extra Credit: Additional regression or analysis
perform ANOVA on average NA sales grouped by top 5 video game genre

```{r}
```