---
title: "hypotheses_testing_vgsales"
output: html_document
---
Reading in and cleaning the data
```{r, include=FALSE}
library(dplyr)
library(e1071)
library(gridExtra)
library(ggplot2)

theme_set(theme_bw())

#reading in the data
df <- read.csv("vgsales.csv")

#since df contains 16k observations, lets limit the data to one year
df <- 
  df %>%
  filter(Year == '2016')

#don't want to visualize games with 0 sales so let's remove that
df <-
  df %>% 
  filter(NA_Sales > 0) 
``` 

Milestone 7: Hypothesis Testing
Decide on and test 3 hypotheses about your data.  You can choose the alpha.  Upload your code to GitHub.  Write a paragraph describing what you tested and summarizing the results of your tests on your website.

```{r}
```

Milestone 8: Regression or other analysis
Perform a statistical analysis of your choice on your data.  This can be computing a regression line, computing one of the previous analyses on a subset of the data, an analysis of variance (ANOVA) test, or any other statistical test.  Write a paragraph briefly describing the analysis and the results on your website and upload the code to GitHub.

>>perform ANOVA on average NA sales grouped by top 3 video game platforms
```{r}
```

Extra Credit: Additional regression or analysis
>>perform ANOVA on average NA sales grouped by top 5 video game genre

```{r}
```