---
title: "exploring_vgsales"
output: html_document
---
Reading in and cleaning the data
```{r, include=FALSE}
library(dplyr)
library(e1071)
library(gridExtra)
library(ggplot2)

#reading in the data
df <- read.csv("vgsales.csv")

#since df contains 16k observations, lets limit the data to one year
df <- 
  df %>%
  filter(Year == '2016')

#don't want to visualize games with 0 sales so let's remove that
df <-
  df %>% 
  filter(NA_Sales > 0) 
``` 
Compute the mean and standard deviation for at least three numerical columns.
Post your code on GitHub and post the means and standard deviations on the webpage.
```{r, include=FALSE}
#Calculating the means of the sales
na_mean <- mean(df$NA_Sales)
eu_mean <- mean(df$EU_Sales)
jp_mean <- mean(df$JP_Sales)

#Calculating the standard deviations of the sales
na_sd <- sd(df$NA_Sales)
eu_sd <- sd(df$EU_Sales)
jp_sd <- sd(df$JP_Sales)

#saving the data into a dataframe
region <- c('North America', 'Europe', 'Japan')
mean <- c(na_mean, eu_mean, jp_mean)
standard_deviation <- c(na_sd, eu_sd, jp_sd)

df1 <- data.frame(region, mean, standard_deviation)

png(filename = "mean_sd.png")
grid.table(df1)
dev.off()
```
Milstone 3 and 4:
For each Numerical Data Column, make one or two plots of the data, using the graph that best represent the data. 
Post the code on Github and the graphs on your webpage.
Write a paragraph summarizing the main features of the data distribution - say the graph exhibits skewness or kurtosis and should be confirmed with quantitative calculations.
```{r, include=FALSE}
na_plot <- 
  df %>%
  ggplot(aes(x = NA_Sales)) +
  geom_bar() +
  xlab('Sales in North America (in millions)') +
  ylab('Number of Games') +
  labs(title = 'Distribution of game sales in North America')

eu_plot <- 
  df %>%
  ggplot(aes(x = EU_Sales)) +
  geom_bar() +
  xlab('Sales in Europe (in millions)') +
  ylab('Number of Games') +
  labs(title = 'Distribution of game sales in Europe')

jp_plot <- 
  df %>%
  ggplot(aes(x = JP_Sales)) +
  geom_bar() +
  xlab('Sales in Japan (in millions)') +
  ylab('Number of Games') +
  labs(title = 'Distribution of game sales in Japan')
```
Looking at whether or not kurtosis or skewness is significant
```{r, include=FALSE}
#Calculating Skewness
na_skew <- skewness(df$NA_Sales)
eu_skew <- skewness(df$EU_Sales)
jp_skew <- skewness(df$JP_Sales)

#Calculating Kurtosis
na_kurt <- kurtosis(df$NA_Sales)
eu_kurt <- kurtosis(df$EU_Sales)
jp_kurt <- kurtosis(df$JP_Sales)

#datasets with skewness larger than 2sqrt(6/n) are substantially skewed
na_skew_thumb <- 2*sqrt(6/length(df$NA_Sales))
eu_skew_thumb <- 2*sqrt(6/length(df$EU_Sales))
jp_skew_thumb <- 2*sqrt(6/length(df$JP_Sales))

#datasets with |kurtosis| larger than 4sqrt(6/n) are substantially different from 0
na_kurt_thumb <- 4*sqrt(6/length(df$NA_Sales))
eu_kurt_thumb <- 4*sqrt(6/length(df$EU_Sales))
jp_kurt_thumb <- 4*sqrt(6/length(df$JP_Sales))

regions <- c('North America', 'Europe', 'Japan')
skewness <- c(na_skew, eu_skew, jp_skew)
kurtosis <- c(na_kurt, eu_kurt, jp_kurt)
skew_thumb <- c(na_skew_thumb, eu_skew_thumb, jp_skew_thumb)
kurt_thumb <- c(na_kurt_thumb, eu_kurt_thumb, jp_kurt_thumb)

df2 <- data.frame(regions,skewness,skew_thumb,kurtosis,kurt_thumb)
png(filename = "shapes.png")
grid.table(df2)
dev.off()
```
Milestone 5: Plotting nominal or ordinal data and comparing data. 
Create a pareto chart of your qualitative data column.  
The dataframe contains 3 qualitative columns: Platform, Genre, and Publisher
```{r, include=FALSE}
#Platform
platform_distribution <-
  df %>%
  ggplot(aes(x = reorder(Platform, -table(Platform)[Platform]))) +
  geom_bar(aes(fill=Platform)) +
  guides(fill=FALSE) +
  xlab('Video Game Platforms') +
  ylab('Frequency') +
  labs(title = 'Distribution of Video Game Platforms')

genre_distribution <-
  df %>%
  ggplot(aes(x = reorder(Genre, -table(Genre)[Genre]), fill=Genre)) +
  guides(fill=FALSE) +
  geom_bar() +
  xlab('Video Game Genre') +
  ylab('Frequency') +
  labs(title = 'Distribution of Video Game Genre')

publisher_distribution <-
  df %>%
  ggplot(aes(x = reorder(Publisher, table(Publisher)[Publisher]))) +
  geom_bar(aes(fill=Publisher)) +
  guides(fill=FALSE) +
  xlab('Video Game Publisher') +
  ylab('Frequency') +
  labs(title = 'Distribution of Video Game Publisher') +
  coord_flip()

```
Milestone 6: Confidence Intervals
Compute the confidence intervals for the means of the three numerical columns. You may choose the confidence level. Upload your code to GitHub, and post the confidence intervals on your webpage. 
```{r}
#We'll use a sample size of 30 since we don't have the entire population of video games
N <- 30

#generating a sample of size 30 for all 3 numerical categories. then calculating respective means. standard deviation, and standard errors
#with a size of 30, use CLT which tells us that mean(df$_Sales) follows a normal distribution with mean(sample_) and standard error approximately sd/sqrt(N)

sNA <- sample(df$NA_Sales, N)
sNA_mean <- mean(sNA)
sNA_sd <- sd(sNA)
sNA_error <- sNA_sd/sqrt(N)

sEU <- sample(df$EU_Sales, N)
sEU_mean <- mean(sEU)
sEU_sd <- sd(sEU)
sEU_error <- sEU_sd/sqrt(N)

sJP <- sample(df$JP_Sales, N)
sJP_mean <- mean(sJP)
sJP_sd <- sd(sJP)
sJP_error <- sJP_sd/sqrt(N)

#defining our confidence interval, we'll use 95%
Q <- qnorm(1 - 0.05/2)

sNA_left_interval <- sNA_mean - Q*sNA_error
sEU_left_interval <- sEU_mean - Q*sEU_error
sJP_left_interval <- sJP_mean - Q*sJP_error

sNA_right_interval <- sNA_mean + Q*sNA_error
sEU_right_interval <- sEU_mean + Q*sEU_error
sJP_right_interval <- sJP_mean + Q*sJP_error

#saving into new dataframe
region <- c('North America', 'Europe', 'Japan')
sample_mean <- c(sNA_mean, sEU_mean, sJP_mean)
sample_standard_deviation <- c(sNA_sd, sEU_sd, sJP_sd)
sample_standard_error <- c(sNA_error, sEU_error, sJP_error)
left_confidence_interval <- c(sNA_left_interval, sEU_left_interval, sJP_left_interval)
right_confidence_interval <- c(sNA_right_interval, sEU_right_interval, sJP_right_interval)

df3 <- data.frame(region, sample_mean, sample_standard_deviation, sample_standard_error, left_confidence_interval, right_confidence_interval)

png(filename = "confidence.png", height = 50*nrow(df3), width = 200*ncol(df3))
grid.table(df3)
dev.off()

```
